Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2016-11-29 bckground.tex
Minor iteration

In this paper we focus on the ATLAS Monte Carlo workflow\mtnote{Are there other
workflows for ATLAS?} and its evolving processes of resource selection.
Traditionally, the ATLAS workflow has been based on single-core tasks, executed
on Grid resources to process large amount (2TB) of input data divided into
discrete I/O units called ``events''. This approach has many merits: (i)
simplified process of resource selection under the assumption of homogeneous
resources and execution environments; (ii) opportunistic distribution of compute
tasks across resources based on contingent availability; (iii) relative
robustness due to the ability of re-executing failed tasks; and (iv)
multi-tiered distribution and storage of events' data.

Despite all the advantages,

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/atlas_workflow.pdf}
  \caption{ATLAS Workflow}
\label{fig:atlas_workflow}
\end{figure}

>>>>

Traditionally, the ATLAS workflow has been based on single-core tasks, executed
on Grid resources to process large amount (2TB) of input data divided into
discrete I/O units called ``events''. This approach has many merits: (i)
simplified process of resource selection under the assumption of homogeneous
resources and execution environments; (ii) opportunistic distribution of compute
tasks across resources based on contingent availability; (iii) relative
robustness due to the ability of re-executing failed tasks; and (iv)
multi-tiered distribution and storage of events' data.

Despite all the advantages, ATLAS workflows have evolved to include
compute-intense tasks that can benefit from multithreaded execution on HPC
machines. The Monte Carlo workflow~\cite{} is one of the largest workflows
executed by the ATLAS experiment and at least one of its stages can benefit from
large amount of parallelism. The Geant4 toolkit is used to simulate the passage
of particles through matter and\ldots

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/atlas_workflow.pdf}
  \caption{ATLAS Monte Carlo workflow.}
\label{fig:atlas_workflow}
\end{figure}
